---
title: "Basic Visualization for Book Coding Projects"
author: "Allison Li"
output: 
  html_document:
    keep_md: true
---

I would like to create some basic visualization for a book coding project. This book coding project is an exploratory study that codes and examines how race/ethnicity is depicted in children's books about race. By investigating both representation of diversity, types of intergroup contacts, acquired information about race and culture, and intergroup bias reduction strategies, this project aims to understand how the present books talks about diversity and build the first step for future studies to investigate whether certain strategy is more effective in media for bias reduction.
One thing I would like to note is that these dataset are from Dr. Katharine Scott, me and Sophie Boyld's project, and some of the codes are already written by Dr. Scott. My project here mainly focuses on the visualization rather than how to analyze some of the research questions.   

```{r load-data, include=FALSE}
library(readxl)
library(tidyverse)
library(writexl)
library(irrCAC)
library(irr)
library(lme4)
library(mclogit)
library(effectsize)
library(car)
library(dplyr)
library(effects)
library(ggplot2)

dWide = read_excel("~/Downloads/charactersWideDataFrameClean (1).xlsx")

dLong = read_excel("~/Downloads/charactersLongDataFrameClean (1).xlsx")

interventions = read_excel("~/Downloads/Final Intervention Codes (2).xlsx")

Comparison = read_excel("~/Downloads/Character_Compare.xlsx")

```

For this portfolio, I would like to first, see the overview information about the books.

## Step 1: visualization of basic book information
### racial/ethnic representation of authors 
Question: What percent of the books had at least one author/illustrator who was each race/ethnicity? This includes people who were biracial/multiracial but who at least partially identified as the selected race.

Asian/Asian American
```{r, echo = F}

table <- table(dWide$asianAuthorIll)
counts <- as.vector(table)
percentages <- counts / sum(counts) * 100

result <- data.frame(
  "AsianAuthorIllustrator" = names(table),
  Count = counts,
  Percentage = percentages
)
print(result)

ggplot(result, aes(x = "", y = Percentage, fill = AsianAuthorIllustrator)) +
  geom_bar(width = 1, stat = "identity") +
  coord_polar("y") +
  geom_text(aes(label = paste0(round(Percentage, 1), "%")), 
            position = position_stack(vjust = 0.5), size = 4) +
  scale_fill_manual(values = c("lightgreen", "#FFEE8c")) +
  labs(title = "Percentage of Books by Asian Author/Illustrator",
       x = NULL, y = NULL)
```

Black
```{r, echo = F}

table <- table(dWide$blackAuthorIll)
counts <- as.vector(table)
percentages <- counts / sum(counts) * 100

result <- data.frame(
  "BlackAuthorIllustrator" = names(table),
  Count = counts,
  Percentage = percentages
)
print(result)

ggplot(result, aes(x = "", y = Percentage, fill = BlackAuthorIllustrator)) +
  geom_bar(width = 1, stat = "identity") +
  coord_polar("y") +
  geom_text(aes(label = paste0(round(Percentage, 1), "%")), 
            position = position_stack(vjust = 0.5), size = 4) +
  scale_fill_manual(values = c("lightgreen", "#FFEE8c")) +
  labs(title = "Percentage of Books by Black Author/Illustrator",
       x = NULL, y = NULL)
```

Hispanic
```{r, echo = F}

table <- table(dWide$hispanicAuthorIll)
counts <- as.vector(table)
percentages <- counts / sum(counts) * 100

result <- data.frame(
  "HispanicAuthorIllustrator" = names(table),
  Count = counts,
  Percentage = percentages
)
print(result)

ggplot(result, aes(x = "", y = Percentage, fill = HispanicAuthorIllustrator)) +
  geom_bar(width = 1, stat = "identity") +
  coord_polar("y") +
  geom_text(aes(label = paste0(round(Percentage, 1), "%")), 
            position = position_stack(vjust = 0.5), size = 4) +
  scale_fill_manual(values = c("lightgreen", "#FFEE8c")) +
  labs(title = "Percentage of Books by Hispanic Author/Illustrator",
       x = NULL, y = NULL)
```

Middle Eastern
```{r, echo = F}

table <- table(dWide$middleEasternIll)
counts <- as.vector(table)
percentages <- counts / sum(counts) * 100

result <- data.frame(
  "MiddleEasternAuthorIllustrator" = names(table),
  Count = counts,
  Percentage = percentages
)
print(result)

ggplot(result, aes(x = "", y = Percentage, fill = MiddleEasternAuthorIllustrator)) +
  geom_bar(width = 1, stat = "identity") +
  coord_polar("y") +
  geom_text(aes(label = paste0(round(Percentage, 1), "%")), 
            position = position_stack(vjust = 0.5), size = 4) +
  scale_fill_manual(values = c("lightgreen", "#FFEE8c")) +
  labs(title = "Percentage of Books by Middle Eastern Author/Illustrator",
       x = NULL, y = NULL)
```

Native American
```{r, echo = F}

table <- table(dWide$nativeAuthorIll)
counts <- as.vector(table)
percentages <- counts / sum(counts) * 100

result <- data.frame(
  "NativeAmericanAuthorIllustrator" = names(table),
  Count = counts,
  Percentage = percentages
)
print(result)

ggplot(result, aes(x = "", y = Percentage, fill = NativeAmericanAuthorIllustrator)) +
  geom_bar(width = 1, stat = "identity") +
  coord_polar("y") +
  geom_text(aes(label = paste0(round(Percentage, 1), "%")), 
            position = position_stack(vjust = 0.5), size = 4) +
  scale_fill_manual(values = c("lightgreen", "#FFEE8c")) +
  labs(title = "Percentage of Books by Native American Author/Illustrator",
       x = NULL, y = NULL)
```

Native Hawaiian / Pacific Islander
```{r, echo = F}

table <- table(dWide$nhpiAuthorIll)
counts <- as.vector(table)
percentages <- counts / sum(counts) * 100

result <- data.frame(
  "NativeHawaiianPacificIslanderAuthorIllustrator" = names(table),
  Count = counts,
  Percentage = percentages
)
print(result)

ggplot(result, aes(x = "", y = Percentage, fill = NativeHawaiianPacificIslanderAuthorIllustrator)) +
  geom_bar(width = 1, stat = "identity") +
  coord_polar("y") +
  geom_text(aes(label = paste0(round(Percentage, 1), "%")), 
            position = position_stack(vjust = 0.5), size = 4) +
  scale_fill_manual(values = c("lightgreen", "#FFEE8c")) +
  labs(title = "Percentage of Books by NHPI Author/Illustrator",
       x = NULL, y = NULL)
```
This could either be lacking representation of NHPI authors/illustrators among the books we examined, or could be that the coders were unable to find further ethnic background information about the authors so they categrized them into Asians or other ethnic racial minority groups. 

White
```{r, echo = F}

table <- table(dWide$whiteAuthorIll)
counts <- as.vector(table)
percentages <- counts / sum(counts) * 100

result <- data.frame(
  "WhiteAuthorIllustrator" = names(table),
  Count = counts,
  Percentage = percentages
)
print(result)

ggplot(result, aes(x = "", y = Percentage, fill = WhiteAuthorIllustrator)) +
  geom_bar(width = 1, stat = "identity") +
  coord_polar("y") +
  geom_text(aes(label = paste0(round(Percentage, 1), "%")), 
            position = position_stack(vjust = 0.5), size = 4) +
  scale_fill_manual(values = c("lightgreen", "#FFEE8c")) +
  labs(title = "Percentage of Books by White Author/Illustrator",
       x = NULL, y = NULL)
```
The general Pie Chart
```{r}
race_cols <- c("blackAuthorIll", "hispanicAuthorIll", "middleEasternIll", 
               "nativeAuthorIll", "nhpiAuthorIll", "whiteAuthorIll", "asianAuthorIll")

##Convert to logical (TRUE/FALSE) in case they are "Yes"/"No"
d_logical <- dWide[, race_cols] == "Yes"

##Sum 
race_counts <- colSums(d_logical)
total_books <- nrow(dWide)
race_percent <- colSums(d_logical) / total_books * 100

##Convert to a data frame for plotting
race_num <- data.frame(
  Race = names(race_counts),
  Count = as.vector(race_counts)
)
race_percentage <- data.frame(
  Race = names(race_percent),
  Percentage = round(as.vector(race_percent), 1)
)

ggplot(race_num, aes(x = reorder(Race, -Count), y = Count, fill = Race)) +
  geom_bar(stat = "identity") +
  labs(title = "Number of Books Featuring Each Ethnic/Racial Group (Author or Illustrator)",
       x = "Ethnic/Racial Group", y = "Number of Books") +
  theme_minimal() +
  theme(legend.position = "none") +
  geom_text(aes(label = Count), vjust = -0.5)

ggplot(race_percentage, aes(x = reorder(Race, -Percentage), y = Percentage, fill = Race)) +
  geom_bar(stat = "identity") +
  geom_text(aes(label = paste0(Percentage, "%")), vjust = -0.5, size = 4) +
  labs(title = "Percentage of Books Featuring Each Ethnic/Racial Group (Author or Illustrator)",
       x = "Ethnic/Racial Group", y = "Percentage of Books") +
  coord_flip() 
```

### Temporal settings of the books
Question: Are the books contemporary, historical, fantastical, or combination of contemporary and historical?

```{r setting}
library(forcats)

table <- table(dWide$temporalSetting)
counts <- as.vector(table)
percentages <- counts / sum(counts) * 100

result <- data.frame(
  "TemporalSetting" = names(table),
  Count = counts,
  Percentage = percentages
)
print(result)

result <- result %>%
  mutate(TemporalSetting = fct_recode(TemporalSetting,
    "Contemporary" = "Contemporary (current day)",
    "Contemporary + Historical" = "Contemporary (current day),Historical",
    "Fantastical/non-human" = "Fantastical/non-human",
    "Historical" = "Historical"
  ))

ggplot(result, aes(x = reorder(TemporalSetting, -Percentage), y = Percentage, fill = TemporalSetting)) +
  geom_bar(stat = "identity") +
  geom_text(aes(label = paste0(round(Percentage, 1), "%")), vjust = -0.5, size = 4) +
  labs(title = "Temporal Setting of Books",
       x = "Setting Type", y = "Percentage of Books") +
  theme_minimal() +
  theme(legend.position = "none")

ggplot(result, aes(x = "", y = Percentage, fill = TemporalSetting)) +
  geom_bar(width = 1, stat = "identity") +
  coord_polar("y") +
  geom_text(aes(label = paste0(round(Percentage, 1), "%")),
            position = position_stack(vjust = 0.5), size = 3.6) +
  labs(title = "Temporal Setting of Books")+
  scale_fill_manual(values = c("Contemporary" = "#d5d1e9", "Contemporary + Historical" = "#d0e4ee", "Fantastical/non-human" = "#F3f5a9", "Historical" = "#f5cf9f"))+
  theme_void()
```
### Fiction/non-fiction/combo
Question: Are the books fiction, non-fiction, or some combination??

```{r setting 2}
table <- table(dWide$fiction)
counts <- as.vector(table)
percentages <- counts / sum(counts) * 100

result <- data.frame(
  "Fiction" = names(table),
  Count = counts,
  Percentage = percentages
)

print(result)

ggplot(result, aes(x = "", y = Percentage, fill = Fiction)) +
  geom_bar(stat = "identity", width = 1) +
  coord_polar("y") +
  geom_text(aes(label = paste0(round(Percentage, 1), "%")),
            position = position_stack(vjust = 0.5), size = 4) +
  scale_fill_manual(values = c("Non-fiction" = "#EDCBD2", "Fiction" = "#C3E0DD", "Combination of fiction and non-fiction" = "#FAE9DA"))+
  labs(title = "Fiction, Nonfiction, or Combination of Both") +
  theme_void()
```

##Step 2: Diversity of characters in the book

This whole chunk is analyzed by Dr. Scott because I am not sure how to do this. According to her "control for the similarities among characters within a particular book, I gave each book a single value for the percent of characters in the book of each race/value/gender/etc. Then we can look at the representation across books that controls for the number of characters in a book." I only copy paste this part because the following analysis needs this part

```{r diversity in the book}
result <- dLong %>%
  # Group by book and race
  group_by(bookID, characterRace) %>%
  # Count occurrences of each race within each book
  summarise(count = n(), .groups = "drop") %>%
  # Calculate total characters per book
  group_by(bookID) %>%
  mutate(total_characters = sum(count),
         percentage = count / total_characters) %>%
  # Pivot to create percentage columns for each race
  pivot_wider(
    id_cols = bookID,
    names_from = characterRace,
    values_from = percentage,
    names_prefix = "characterRacePercent",
    values_fill = 0
  )

# Join the results back to the original dataframe and create dLongChar
dLongChar <- dLong %>%
  left_join(result, by = "bookID")

```

```{r, include = F}

# Calculate percentages for character valence
result <- dLongChar %>%
  # Group by book and valence
  group_by(bookID, characterValence) %>%
  # Count occurrences of each valence within each book
  summarise(count = n(), .groups = "drop") %>%
  # Calculate total characters per book
  group_by(bookID) %>%
  mutate(total_characters = sum(count),
         percentage = count / total_characters) %>%
  # Pivot to create percentage columns for each valence
  pivot_wider(
    id_cols = bookID,
    names_from = characterValence,
    values_from = percentage,
    names_prefix = "characterValencePercent",
    values_fill = 0
  )

# Join the results back to the original dataframe and overwrite dLongChar
dLongChar <- dLongChar %>%
  left_join(result, by = "bookID")

```

```{r, include = F}

# Calculate percentages for character centrality
result <- dLongChar %>%
  # Group by book and centrality
  group_by(bookID, characterCentrality) %>%
  # Count occurrences of each centrality within each book
  summarise(count = n(), .groups = "drop") %>%
  # Calculate total characters per book
  group_by(bookID) %>%
  mutate(total_characters = sum(count),
         percentage = count / total_characters) %>%
  # Pivot to create percentage columns for each centrality
  pivot_wider(
    id_cols = bookID,
    names_from = characterCentrality,
    values_from = percentage,
    names_prefix = "characterCentralityPercent",
    values_fill = 0
  )

# Join the results back to the original dataframe and overwrite dLongChar
dLongChar <- dLongChar %>%
  left_join(result, by = "bookID")

```

```{r, include = F}

# Calculate percentages for character gender
result <- dLongChar %>%
  # Group by book and gender
  group_by(bookID, characterGender) %>%
  # Count occurrences of each gender within each book
  summarise(count = n(), .groups = "drop") %>%
  # Calculate total characters per book
  group_by(bookID) %>%
  mutate(total_characters = sum(count),
         percentage = count / total_characters) %>%
  # Pivot to create percentage columns for each gender
  pivot_wider(
    id_cols = bookID,
    names_from = characterGender,
    values_from = percentage,
    names_prefix = "characterGenderPercent",
    values_fill = 0
  )

# Join the results back to the original dataframe and overwrite dLongChar
dLongChar <- dLongChar %>%
  left_join(result, by = "bookID")

```

```{r, include = F}

# Calculate percentages for character gender conformity
result <- dLongChar %>%
  # Group by book and gender conformity
  group_by(bookID, characterGenderConf) %>%
  # Count occurrences of each gender conformity within each book
  summarise(count = n(), .groups = "drop") %>%
  # Calculate total characters per book
  group_by(bookID) %>%
  mutate(total_characters = sum(count),
         percentage = count / total_characters) %>%
  # Pivot to create percentage columns for each gender conformity
  pivot_wider(
    id_cols = bookID,
    names_from = characterGenderConf,
    values_from = percentage,
    names_prefix = "characterGenderConfPercent",
    values_fill = 0
  )

# Clean column names
names(result) <- names(result) %>%
  make.names() %>%
  str_remove_all("\\.")

# Join the results back to the original dataframe and overwrite dLong
dLongChar <- dLongChar %>%
  left_join(result, by = "bookID")


```

```{r, include = F}

# Calculate percentages for character age
result <- dLongChar %>%
  # Group by book and age
  group_by(bookID, characterAge) %>%
  # Count occurrences of each age category within each book
  summarise(count = n(), .groups = "drop") %>%
  # Calculate total characters per book
  group_by(bookID) %>%
  mutate(total_characters = sum(count),
         percentage = count / total_characters) %>%
  # Pivot to create percentage columns for each age category
  pivot_wider(
    id_cols = bookID,
    names_from = characterAge,
    values_from = percentage,
    names_prefix = "characterAgePercent",
    values_fill = 0
  )

# Clean column names
names(result) <- names(result) %>%
  make.names() %>%
  str_remove_all("\\.") %>%
  str_replace_all("\\s", "")

# Join the results back to the original dataframe and overwrite dLong
dLongChar <- dLongChar %>%
  left_join(result, by = "bookID")

```

```{r, include = F}

# Select only between-book columns and only one row per book to do some basic summarizing. 

dW = dLongChar %>%
  select(characterNumber, book:allBlackCreators, characterRacePercentA:characterAgePercentunclear) %>%
  filter(characterNumber == 1) %>%
  select(-characterNumber)

```

**Main Question: Who is captured in children’s books about race**

### Race diversity of each character per book

```{r race character}
#Create a vector of column names
columns <- c("characterRacePercentW", "characterRacePercentB", "characterRacePercentambi", 
             "characterRacePercentH", "characterRacePercentNative", "characterRacePercentA", 
             "characterRacePercentME", "characterRacePercentmulti", "characterRacePercentNHPI")

#Create an empty dataframe to store results
result_table <- data.frame(Column = columns,
                           Mean = numeric(length(columns)),
                           SD = numeric(length(columns)))

#Calculate mean and SD for each column
for (i in 1:length(columns)) {
  result_table$Mean[i] <- mean(dW[[columns[i]]], na.rm = TRUE)
  result_table$SD[i] <- sd(dW[[columns[i]]], na.rm = TRUE)
}

#Round the results to 2 decimal places
result_table$Mean <- round(result_table$Mean, 2)
result_table$SD <- round(result_table$SD, 2)

#Print the resulting table
print(result_table)


#Plot!
result_table$Race <- c("White", "Black", "Ambiguous", "Latinx", "Native", 
                       "Asian", "Middle Eastern", "Multiracial", "NHPI")

ggplot(result_table, aes(x = reorder(Race, -Mean), y = Mean)) +
  geom_bar(stat = "identity", fill = "lightblue") +
  geom_errorbar(aes(ymin = Mean - SD, ymax = Mean + SD), width = 0.2) +
  labs(title = "Average Racial Representation of Characters per Book",
       x = "Character Race",
       y = "Mean Percentage of Characters") +
  theme_minimal()
```

### Valence representation of each character per book

```{r valence character}
columns <- c("characterValencePercentpos", "characterValencePercentneg", "characterValencePercentneut", "characterValencePercentmix")

#Create an empty dataframe to store results
result_table <- data.frame(Column = columns,
                           Mean = numeric(length(columns)),
                           SD = numeric(length(columns)))

#Calculate mean and SD for each column
for (i in 1:length(columns)) {
  result_table$Mean[i] <- mean(dW[[columns[i]]], na.rm = TRUE)
  result_table$SD[i] <- sd(dW[[columns[i]]], na.rm = TRUE)
}

#Round the results to 2 decimal places
result_table$Mean <- round(result_table$Mean, 2)
result_table$SD <- round(result_table$SD, 2)

#Print the resulting table
print(result_table)

#Plot again!
result_table$Column <- c()

ggplot(result_table, aes(x = reorder(columns, -Mean), y = Mean)) +
  geom_bar(stat = "identity", fill = "lightblue") +
  geom_errorbar(aes(ymin = Mean - SD, ymax = Mean + SD), width = 0.2) +
  labs(title = "Average Valence of Each Character per Book",
       x = "Character Valence",
       y = "Mean Percentage of Characters") +
  scale_x_discrete(labels = c(
    "characterValencePercentpos" = "Positive",
    "characterValencePercentneg" = "Negative",
    "characterValencePercentneut" = "Neutral",
    "characterValencePercentmix" = "Mixed"
  )) +
  theme_minimal()
```

###Gender of each race depicted in the books

```{r gender character}
columns <- c("characterGenderPercentfemale", "characterGenderPercentmale", "characterGenderPercentunclear")

#Create an empty dataframe to store results
result_table <- data.frame(Column = columns,
                           Mean = numeric(length(columns)),
                           SD = numeric(length(columns)))

#Calculate mean and SD for each column
for (i in 1:length(columns)) {
  result_table$Mean[i] <- mean(dW[[columns[i]]], na.rm = TRUE)
  result_table$SD[i] <- sd(dW[[columns[i]]], na.rm = TRUE)
}

#Round the results to 2 decimal places
result_table$Mean <- round(result_table$Mean, 2)
result_table$SD <- round(result_table$SD, 2)

#Print the resulting table
print(result_table)

#Plot again!
result_table$Column <- c()

ggplot(result_table, aes(x = reorder(columns, -Mean), y = Mean)) +
  geom_bar(stat = "identity", fill = "#f5cf9f") +
  geom_errorbar(aes(ymin = Mean - SD, ymax = Mean + SD), width = 0.2) +
  labs(title = "Average Valence of Each Character per Book",
       x = "Character Valence",
       y = "Mean Percentage of Characters") +
  scale_x_discrete(labels = c(
    "characterGenderPercentfemale" = "female",
    "characterGenderPercentmale" = "male",
    "characterGenderPercentunclear" = "unclear"
  )) +
  theme_minimal()
```

##Step 3: Intervention Strategies in the books

We have included four main intervention strategies that might be depicted in the book to reduce intergroup racial bias, which are intergroup contact, individuation, perspective taking, and positive exemplars. 

### presence of intergroup contact

**What percentage of books depicted intergroup contact?**

```{r}
interventions_clean <- interventions %>%
  filter(!is.na(contact))

table <- table(interventions_clean$contact)
counts <- as.vector(table)
percentages <- counts / sum(counts) * 100

result <- data.frame(
  "contact" = names(table),
  Count = counts,
  Percentage = percentages
)
print(result)
```
**What percentage of books depicted intergroup contact between children**

```{r children intergroup contact}
table <- table(interventions$contactChildren)
counts <- as.vector(table)
percentages <- counts / sum(counts) * 100

result <- data.frame(
  "Contact Between Children" = names(table),
  Count = counts,
  Percentage = percentages
)
print(result)
```

**What percentage of books depict intergroup contact between children, between adults, and between children and adult?**

```{r types of contact}

library(dplyr)
library(tidyr)

contact_long <- interventions %>%
  dplyr::select(contactChildren, contactAdults, contactChildAdult) %>%
  pivot_longer(cols = everything(),
               names_to = "ContactType",
               values_to = "Presence") %>%
  filter(!is.na(Presence)) %>%
  dplyr::mutate(ContactType = dplyr::recode(ContactType,
                              "contactChildren" = "Children",
                              "contactAdults" = "Adults",
                              "contactChildAdult" = "Child + Adult"),
         Presence = dplyr::recode(as.character(Presence),
                           "1" = "Yes",
                           "0" = "No"))
contact_summary <- contact_long %>%
  group_by(ContactType, Presence) %>%
  summarise(Count = n(), .groups = "drop") %>%
  group_by(ContactType) %>%
  mutate(Percentage = Count / sum(Count) * 100,
         Label = paste0(Presence, "\n", round(Percentage, 1), "%"))

ggplot(contact_summary, aes(x = "", y = Percentage, fill = Presence)) +
  geom_bar(stat = "identity", width = 1) +
  coord_polar("y") +
  geom_text(aes(label = Label),
            position = position_stack(vjust = 0.5),
            size = 3, color = "black") +
  facet_wrap(~ ContactType) +
  scale_fill_manual(values = c("No" = "#d5d1e9", "Yes" = "#d0e4ee")) +
  labs(title = "Presence of Intergroup Contact Types in Books",
       fill = "Contact Present") +
  theme_void() +
  theme(
    strip.background = element_rect(fill = "gray90"),
    strip.text = element_text(size = 12, face = "bold"),
    legend.position = "bottom"
  )
```

### presence of perspective taking

**What percentage of books depicted perspective taking?**

```{r total pt}
interventions <- interventions %>%
  mutate(pt_any = if_else(
    emotionsBasic == 1 | emotionsDiscrim == 1 | emotionsPT == 1 | emotionsPT2 == 1,
    1, 0
  ))

##four codes for PT
interventions %>%
  summarise(percent_with_PT = round(mean(pt_any == 1, na.rm = TRUE) * 100, 1))
pt_vars <- c("emotionsBasic", "emotionsDiscrim", "emotionsPT", "emotionsPT2")

#Reshape to long format
pt_long <- interventions %>%
  select(all_of(pt_vars)) %>%
  pivot_longer(cols = everything(),
               names_to = "PerspectiveType",
               values_to = "Present") %>%
  filter(!is.na(Present))  # remove any missing values

##Summarize the percent of books with each type
pt_summary <- pt_long %>%
  group_by(PerspectiveType) %>%
  summarise(
    Count = sum(Present == 1),
    Total = n(),
    Percentage = round(Count / Total * 100, 1),
    .groups = "drop"
  )

print(pt_summary)


#Plot~~
pt_summary$PerspectiveType <- dplyr::recode(pt_summary$PerspectiveType,
  "emotionsBasic" = "Emotion highlighted",
  "emotionsDiscrim" = "Feelings of Discrimination",
  "emotionsPT" = "Perspective Taking Implicit",
  "emotionsPT2" = "Perspective Taking Explicit"
)

# Create bar plot
ggplot(pt_summary, aes(x = reorder(PerspectiveType, -Percentage), y = Percentage, fill = PerspectiveType)) +
  geom_bar(stat = "identity") +
  geom_text(aes(label = paste0(Percentage, "%")), vjust = -0.5, size = 3) +
  labs(
    title = "Percentage of Books Showing Each Type of Perspective Taking",
    x = "Perspective-Taking Type",
    y = "Percentage of Books"
  ) +
  scale_fill_manual(values = c("Emotion highlighted" = "#EDCBD2", "Feelings of Discrimination" = "#C3E0DD", "Perspective Taking Implicit" = "#FAE9DA", "Perspective Taking Explicit" = "#d5d1e9"))+
  theme_minimal() +
  theme(
    axis.text.x = element_text(angle = 30, hjust = 1),
    legend.position = "none"
  )
```

### presence of positive exemplars



### presence of individuation

**Percentage of perceptual individuation presented**

```{r perindi}
table <- table(interventions$perceptualIndiv)
counts <- as.vector(table)
percentages <- counts / sum(counts) * 100

result <- data.frame(
  "perceptualIndividuation" = names(table),
  Count = counts,
  Percentage = percentages
)
print(result)


# Plot
ggplot(result, aes(x = "", y = Percentage, fill = perceptualIndividuation)) +
  geom_bar(stat = "identity", width = 1) +
  coord_polar("y") +
  geom_text(aes(label = paste0(round(Percentage, 1), "%")),
            position = position_stack(vjust = 0.5), size = 3.5, color = "black") +
  scale_fill_manual(values = c("1" = "#f5a7a6", "0" = "#f3f5a9"),
                    labels = c("0" = "Not Present", "1" = "Present")) +
  labs(title = "Perceptual Individuation in Books",
       fill = "Perceptual Individuation") +
  theme_void()
```

**Percentage of perceptual individuation presented**

```{r concepindi}
table <- table(interventions$conceptualIndiv)
counts <- as.vector(table)
percentages <- counts / sum(counts) * 100

result <- data.frame(
  "conceptualIndividuation" = names(table),
  Count = counts,
  Percentage = percentages
)
print(result)

# Plot
ggplot(result, aes(x = "", y = Percentage, fill = conceptualIndividuation)) +
  geom_bar(stat = "identity", width = 1) +
  coord_polar("y") +
  geom_text(aes(label = paste0(round(Percentage, 1), "%")),
            position = position_stack(vjust = 0.5), size = 3.5, color = "black") +
  scale_fill_manual(values = c("1" = "#f5a7a6", "0" = "#f3f5a9"),
                    labels = c("0" = "Not Present", "1" = "Present")) +
  labs(title = "Conceptual Individuation in Books",
       fill = "Conceptual Individuation") +
  theme_void()
```

##Step 4: Knowledge Aquisition
### Knowledge Acquisition  

We coded for seven types of knowledge that might be presented in the books, including: Information about current racial inequality or contemporary prejudice; Information about historical racism; information about what race is (e.g., teaching about melanin, social construction of race, different skin colors); Information about culture (e.g., explaining what the cultural markers are, why they are important, social norms/practices in a group); Information on anti-racist values and norms; Information on structural racism (e.g., "Because of unfair rules that were made up a long time ago, there are differences in how these groups are treated today." or Addressing racism in an institution.); and Information on police violence/brutality. I would like to know what types are presented in the book, and if different time setting of the books might have more certain types of knowledge presented. For example, would historical books have more information about historical racism, while contemporary have more information about anti-racist value?

**Information about current racial inequality or contemporary prejudice**

```{r}

table <- table(interventions$contempPrej)
counts <- as.vector(table)
percentages <- counts / sum(counts) * 100

result <- data.frame(
  "contemporaryPrejudice" = names(table),
  Count = counts,
  Percentage = percentages
)
print(result)

```
**Information about historical racism**

```{r, echo = F}

table <- table(interventions$historicalPrej)
counts <- as.vector(table)
percentages <- counts / sum(counts) * 100

result <- data.frame(
  "historicalRacism" = names(table),
  Count = counts,
  Percentage = percentages
)
print(result)

```

**Information about what race is**

```{r, echo = F}

table <- table(interventions$knowRace)
counts <- as.vector(table)
percentages <- counts / sum(counts) * 100

result <- data.frame(
  "raceKnowledge" = names(table),
  Count = counts,
  Percentage = percentages
)
print(result)

```

**Information about culture**

```{r, echo = F}

table <- table(interventions$knowCulture)
counts <- as.vector(table)
percentages <- counts / sum(counts) * 100

result <- data.frame(
  "cultureKnowledge" = names(table),
  Count = counts,
  Percentage = percentages
)
print(result)

```

**Information on anti-racist values and norms**

```{r, echo = F}

table <- table(interventions$antiRacism)
counts <- as.vector(table)
percentages <- counts / sum(counts) * 100

result <- data.frame(
  "antiRacistValues" = names(table),
  Count = counts,
  Percentage = percentages
)
print(result)

```

**Information on structural racism**

```{r, echo = F}

table <- table(interventions$structuralRacism)
counts <- as.vector(table)
percentages <- counts / sum(counts) * 100

result <- data.frame(
  "structuralRacism" = names(table),
  Count = counts,
  Percentage = percentages
)
print(result)

```

**Information on police violence/brutality**

```{r, echo = F}

table <- table(interventions$policeViolence)
counts <- as.vector(table)
percentages <- counts / sum(counts) * 100

result <- data.frame(
  "policeViolence" = names(table),
  Count = counts,
  Percentage = percentages
)
print(result)

```

**Total Visualization**

```{r total visualization}
knowledge_vars <- c("contempPrej", "historicalPrej", "knowRace", 
                    "knowCulture", "antiRacism", "structuralRacism", "policeViolence")

# Convert to long format and calculate percentages
knowledge_long <- interventions %>%
  dplyr::select(all_of(knowledge_vars)) %>%
  pivot_longer(cols = everything(), names_to = "KnowledgeType", values_to = "Present") %>%
  filter(!is.na(Present)) %>%
  group_by(KnowledgeType) %>%
  summarise(
    Count = sum(Present == 1),
    Total = n(),
    Percentage = round(Count / Total * 100, 1),
    .groups = "drop"
  )

knowledge_long$KnowledgeType <- dplyr::recode(knowledge_long$KnowledgeType,
  "contempPrej" = "Contemporary Prejudice",
  "historicalPrej" = "Historical Racism",
  "knowRace" = "What Race Is",
  "knowCulture" = "Culture",
  "antiRacism" = "Anti-Racist Values",
  "structuralRacism" = "Structural Racism",
  "policeViolence" = "Police Violence"
)

ggplot(knowledge_long, aes(x = reorder(KnowledgeType, -Percentage), y = Percentage, fill = KnowledgeType)) +
  geom_bar(stat = "identity") +
  geom_text(aes(label = paste0(Percentage, "%")), vjust = -0.5, size = 3) +
  labs(
    title = "Types of Knowledge Presented in Children's Books",
    x = "Knowledge Type",
    y = "Percentage of Books"
  ) +
  scale_fill_manual(values = c("Contemporary Prejudice" = "#ffcbe1", "Historical Racism" = "#d6e5bd", "What Race Is" = "#f9e1a8", "Culture" = "#bcd8ec", "Anti-Racist Values" = "#dcccec", "Structural Racism" = "#ffdab4", "Police Violence" = "#e5ecf8")) +
  theme_minimal() +
  theme(
    axis.text.x = element_text(angle = 30, hjust = 1),
    legend.position = "none"
  )
```

Based on the graph, it is clear that the most mentioned knowledge in children's book about race is anti-racist value. This shows that the creatie team believe the most important thing for children to get out from the books would be values that promote equality and active information towards racial prejudice or discrimination. The least mentioned is police violence, which makes sense because that would not be the focus of the books. Interesting, what is race is the second lowest, which might suggests that children's books might focus less on educating and talking about race by teaching children about what does race mean.  

