---
title: "Thesis data Main Analysis"
author: "Allison Li"
date: "03242025"
output: 
  html_document:
    encoding: UTF-8
    toc: true
    number_sections: false
    toc_float: true
    toc_depth: 4
    fig_caption: true
---

> The projects should be numbered consecutively (i.e., in the order in which you began them), and should include for each project a description of the goal, the product (computer program, hand graph, computer graph, etc.), the data, and some interpretation. Reports must be reproducible and of high quality in terms of writing, grammar, presentation, etc.

## Bullshit Frequency scales and other variables's partial correlation when controled for lying tendency
```{r BFS and others}
##BFS and BPS
partial_BFSBPS <- Thesis_scale %>% 
  select(bfsmean, bpsmean, liemean) %>%
  drop_na()

partial_BFSBPS_result <- pcor.test(partial_BFSBPS$bfsmean, 
                                 partial_BFSBPS$bpsmean, 
                                 partial_BFSBPS$liemean)

print(partial_corr_result)

##BFS and mach
partial_BFSmach<- Thesis_scale %>% 
  select(bfsmean, sdtmachmean, liemean) %>% 
  drop_na()

partial_BFSmach_result <- pcor.test(partial_BFSmach$bfsmean, 
                                 partial_BFSmach$sdtmachmean, 
                                 partial_BFSmach$liemean)

print(partial_BFSmach_result)

##BFS and narc
partial_BFSnarc<- Thesis_scale %>% 
  select(bfsmean, sdtnarcmean, liemean) %>% 
  drop_na()

partial_BFSnarc_result <- pcor.test(
  x = partial_BFSnarc$bfsmean,
  y = partial_BFSnarc$sdtnarcmean,
  z = partial_BFSnarc$liemean)

print(partial_BFSnarc_result)

##BFS and psychopathy
partial_BFSpsych<- Thesis_scale %>% 
  select(bfsmean, sdtpsychmean, liemean) %>%
  drop_na()

partial_BFSpsych_result <- pcor.test(
  x = partial_BFSpsych$bfsmean,
  y = partial_BFSpsych$sdtpsychmean,
  z = partial_BFSpsych$liemean
  )

print(partial_BFSpsych_result)



```

## Bullshit Propensity scales and other variables's partial correlation when controled for lying tendency
```{r BPS and others}
##BPS and mach
partial_BPSmach<- Thesis_scale %>% 
  select(bpsmean, sdtmachmean, liemean) %>%
  drop_na()

partial_BPSmach_result <- pcor.test(
  x = partial_BPSmach$bpsmean,
  y = partial_BPSmach$sdtmachmean,
  z = partial_BPSmach$liemean
  )

print(partial_BPSmach_result)

##BPS and narc
partial_BPSnarc<- Thesis_scale %>% 
  select(bpsmean, sdtnarcmean, liemean) %>%
  drop_na()

partial_BPSnarc_result <- pcor.test(
  x = partial_BPSnarc$bpsmean,
  y = partial_BPSnarc$sdtnarcmean,
  z = partial_BPSnarc$liemean
  )

print(partial_BPSnarc_result)

##BPS and psychopathy
partial_BPSpsych<- Thesis_scale %>% 
  select(bpsmean, sdtpsychmean, liemean) %>%
  drop_na()

partial_BPSpsych_result <- pcor.test(
  x = partial_BPSpsych$bpsmean,
  y = partial_BPSpsych$sdtpsychmean,
  z = partial_BPSpsych$liemean
  )

print(partial_BPSpsych_result)
```

```{r}
percenrage correct
```
