---
title: "Thesis data descriptives and demographic information"
author: "Allison Li"
date: "03222025"
output: 
  html_document:
    encoding: UTF-8
    toc: true
    number_sections: false
    toc_float: true
    toc_depth: 4
    fig_caption: true
---
## Goal
For this portfolio, I will continue to use the dataset from my thesis study. This portfolio will focus on analyzing the descriptive information for each scale and visual representation of the demographic information for the participants.

```{r}
##install packages
##install.packages(c("tidytext", "stringr"))
library(tidytext)
library(psych)
library(ggplot2)
library(ltm)
library(ppcor)
library(tidyverse)
library(haven)
library(stringr)
library(dplyr)
Thesis_scale <- readRDS("Thesis_scale.rds")
```

## Step 1: calculating scales' basic descriptives (mean, sd, max, and mix) and cronbach alpha
```{r cronbach alpha and other descriptives for each scales}
##Bullshit Frequency scale general  
bfs <- c("BFS_1", "BFS_2", "BFS_3", "BFS_4", "BFS_5", "BFS_6", "BFS_7", "BFS_8", "BFS_9", "BFS_10", "BFS_11", "BFS_12")
Thesis_scale <- Thesis_scale %>%
  mutate(BFS_score = rowMeans(Thesis_scale[,bfs],na.rm=TRUE)) 
bfs_items <- Thesis_scale[, bfs]
cronbach.alpha(bfs_items, standardized = TRUE, CI = TRUE, na.rm = TRUE)

##Bullshit Frequency scale evasive
bfse <- c("BFS_9", "BFS_10", "BFS_11", "BFS_12")
Thesis_scale <- Thesis_scale %>%
  mutate(BFSe_score = rowMeans(Thesis_scale[,bfse],na.rm=TRUE)) 
bfse_items <- Thesis_scale[, bfse]
cronbach.alpha(bfse_items, standardized = TRUE, CI = TRUE, na.rm = TRUE)

##Bullshit Frequency scale persuasive
bfsp <- c("BFS_1", "BFS_2", "BFS_3", "BFS_4", "BFS_5", "BFS_6", "BFS_7", "BFS_8")
Thesis_scale <- Thesis_scale %>%
  mutate(BFSp_score = rowMeans(Thesis_scale[,bfsp],na.rm=TRUE))
bfsp_items <- Thesis_scale[, bfsp]
cronbach.alpha(bfsp_items, standardized = TRUE, CI = TRUE, na.rm = TRUE)

##Bullshit Propensity scale 
bps <- c("BPS_1", "BPS_2", "BPS_3", "BPS_4", "BPS_5", "BPS_6", "BPS_7", "BPS_8", "BPS_9", "BPS_10", "BPS_11", "BPS_12")
Thesis_scale <- Thesis_scale %>%
  mutate(BPS_score = rowMeans(Thesis_scale[,bps],na.rm=TRUE))
bps_items <- Thesis_scale[, bps]
cronbach.alpha(bps_items, standardized = TRUE, CI = TRUE, na.rm = TRUE)

##Lying in Everyday Situations Scale
lie <- c("lies1", "lies2", "lies3", "lies4", "lies5", "lies6", "lies7", "lies8", "lies9", "lies10", "lies11", "lies12", "lies13", "lies14")
Thesis_scale <- Thesis_scale %>%
  mutate(LIE_score = rowMeans(Thesis_scale[,lie],na.rm=TRUE))
lie_items <- Thesis_scale[, lie]
cronbach.alpha(lie_items, standardized = TRUE, CI = TRUE, na.rm = TRUE)

##Short_dark_triad Narcissism
sdtnarc <- c("DTS_Nar_1", "DTS_Nar_2", "DTS_Nar_3", "DTS_Nar_4", "DTS_Nar_5", "DTS_Nar_6", "DTS_Nar_7", "DTS_Nar_8", "DTS_Nar_9")
Thesis_scale <- Thesis_scale %>%
  mutate(sdtnarc_score = rowMeans(Thesis_scale[,sdtnarc],na.rm=TRUE))
sdtnarc_items <- Thesis_scale[, sdtnarc]
cronbach.alpha(sdtnarc_items, standardized = TRUE, CI = TRUE, na.rm = TRUE)

##Short_dark_triad Machiavellianism
sdtmach <- c("DTS_MACH_1", "DTS_MACH_2", "DTS_MACH_3", "DTS_MACH_4", "DTS_MACH_5", "DTS_MACH_6", "DTS_MACH_7", "DTS_MACH_8", "DTS_MACH_9")
Thesis_scale <- Thesis_scale %>%
  mutate(sdtmach_score = rowMeans(Thesis_scale[,sdtmach],na.rm=TRUE))
sdtmach_items <- Thesis_scale[, sdtmach]
cronbach.alpha(sdtmach_items, standardized = TRUE, CI = TRUE, na.rm = TRUE)

##Short_dark_triad Psychopathy
sdtpsych <- c("DTS_Path_1", "DTS_Path_2", "DTS_Path_3", "DTS_Path_4", "DTS_Path_5", "DTS_Path_6", "DTS_Path_7", "DTS_Path_8", "DTS_Path_9")
Thesis_scale <- Thesis_scale %>%
  mutate(sdtpsych_score = rowMeans(Thesis_scale[,sdtpsych],na.rm=TRUE))
sdtpsych_items <- Thesis_scale[, sdtpsych]
cronbach.alpha(sdtpsych_items, standardized = TRUE, CI = TRUE, na.rm = TRUE)

##Narcissistic Personality Inventory
narc <- c("NPI_1", "NPI_2", "NPI_3", "NPI_4", "NPI_5", "NPI_6", "NPI_7", "NPI_8", "NPI_9", "NPI_10", "NPI_11", "NPI_12", "NPI_13", "NPI_14", "NPI_15", "NPI_16")
Thesis_scale <- Thesis_scale %>%
  mutate(narc_score = rowMeans(Thesis_scale[,narc],na.rm=TRUE))
narc_items <- Thesis_scale[, narc]
cronbach.alpha(narc_items, standardized = TRUE, CI = TRUE, na.rm = TRUE)

##Machiavellianism Personality scale
mach <- c("MPS_1", "MPS_2", "MPS_3", "MPS_4", "MPS_5", "MPS_6", "MPS_7", "MPS_8", "MPS_9", "MPS_10", "MPS_11", "MPS_12", "MPS_13", "MPS_14", "MPS_15", "MPS_16")
Thesis_scale <- Thesis_scale %>%
  mutate(mach_score = rowMeans(Thesis_scale[,mach],na.rm=TRUE))
mach_items <- Thesis_scale[, mach]
cronbach.alpha(mach_items, standardized = TRUE, CI = TRUE, na.rm = TRUE)

##Levenson Self-Report Psychopathy Scale
psycho <- c("LSRP_PPS_1", "LSRP_PPS_2", "LSRP_PPS_3", "LSRP_PPS_4", "LSRP_PPS_5", "LSRP_PPS_6", "LSRP_PPS_7", "LSRP_PPS_8", "LSRP_PPS_9", "LSRP_PPS_10", "LSRP_PPS_11", "LSRP_PPS_12", "LSRP_PPS_13", "LSRP_PPS_14", "LSRP_PPS_15", "LSRP_PPS_16", "LSRP_SPS_1", "LSRP_SPS_2", "LSRP_SPS_3", "LSRP_SPS_4", "LSRP_SPS_5", "LSRP_SPS_6", "LSRP_SPS_7", "LSRP_SPS_8", "LSRP_SPS_9", "LSRP_SPS_10")
Thesis_scale <- Thesis_scale %>%
  mutate(psycho_score = rowMeans(Thesis_scale[,psycho],na.rm=TRUE)) 
psycho_items <- Thesis_scale[, psycho]
cronbach.alpha(psycho_items, standardized = TRUE, CI = TRUE, na.rm = TRUE)

##primary factor of psychopathy scale
psychopri <- c("LSRP_PPS_1", "LSRP_PPS_2", "LSRP_PPS_3", "LSRP_PPS_4", "LSRP_PPS_5", 
                    "LSRP_PPS_6", "LSRP_PPS_7", "LSRP_PPS_8", "LSRP_PPS_9", "LSRP_PPS_10", 
                    "LSRP_PPS_11", "LSRP_PPS_12", "LSRP_PPS_13", "LSRP_PPS_14", "LSRP_PPS_15", 
                    "LSRP_PPS_16")
Thesis_scale <- Thesis_scale %>%
  mutate(psychopri_score = rowMeans(Thesis_scale[,psychopri],na.rm=TRUE)) 
psychopri_items <- Thesis_scale[, psychopri]
cronbach.alpha(psychopri_items, standardized = TRUE, CI = TRUE, na.rm = TRUE)

##secondary factor of psychopathy scale
psychosec <- c("LSRP_SPS_1", "LSRP_SPS_2", "LSRP_SPS_3", "LSRP_SPS_4", "LSRP_SPS_5", 
                    "LSRP_SPS_6", "LSRP_SPS_7", "LSRP_SPS_8", "LSRP_SPS_9", "LSRP_SPS_10")
Thesis_scale <- Thesis_scale %>%
  mutate(psychosec_score = rowMeans(Thesis_scale[,psychosec],na.rm=TRUE)) 
psychosec_items <- Thesis_scale[, psychosec]
cronbach.alpha(psychosec_items, standardized = TRUE, CI = TRUE, na.rm = TRUE)

##Self-esteem (Rosenberg)
se <- c("self_esteem_1", "self_esteem_2", "self_esteem_3", "self_esteem_4", "self_esteem_5", 
                     "self_esteem_6", "self_esteem_7", "self_esteem_8", "self_esteem_9", "self_esteem_10")
Thesis_scale <- Thesis_scale %>%
  mutate(se_score = rowMeans(Thesis_scale[,se],na.rm=TRUE)) 
se_items <- Thesis_scale[, se]
cronbach.alpha(se_items, standardized = TRUE, CI = TRUE, na.rm = TRUE)

##HEXACO
##Honesty_humility
hon <- c("hex6", "hex12", "hex18", "hex24", "hex30", "hex36", "hex42", "hex48", "hex54", "hex60")
Thesis_scale <- Thesis_scale %>%
  mutate(hon_score = rowMeans(Thesis_scale[,hon],na.rm=TRUE)) 
hon_items <- Thesis_scale[, hon]
cronbach.alpha(hon_items, standardized = TRUE, CI = TRUE, na.rm = TRUE)

##Emotionality
emo <- c("hex5", "hex11", "hex17", "hex23", "hex29", "hex35", "hex41", "hex47", "hex53", "hex59")
Thesis_scale <- Thesis_scale %>%
  mutate(emo_score = rowMeans(Thesis_scale[,emo],na.rm=TRUE)) 
emo_items <- Thesis_scale[, emo]
cronbach.alpha(emo_items, standardized = TRUE, CI = TRUE, na.rm = TRUE)

##Extraversion
extra <- c("hex4", "hex10", "hex16", "hex22", "hex28", "hex34", "hex40", "hex46", "hex52", "hex58")
Thesis_scale <- Thesis_scale %>%
  mutate(extra_score = rowMeans(Thesis_scale[,extra],na.rm=TRUE)) 
extra_items <- Thesis_scale[, extra]
cronbach.alpha(extra_items, standardized = TRUE, CI = TRUE, na.rm = TRUE)

##Agreeableness
agree <- c("hex3", "hex9", "hex15", "hex21", "hex27", "hex33", "hex39", "hex45", "hex51", "hex57")
Thesis_scale <- Thesis_scale %>%
  mutate(agree_score = rowMeans(Thesis_scale[,agree],na.rm=TRUE)) 
agree_items <- Thesis_scale[, agree]
cronbach.alpha(agree_items, standardized = TRUE, CI = TRUE, na.rm = TRUE)

##CONSCIENTIOUSNESS
cons <- c("hex2", "hex8", "hex14", "hex20", "hex26", "hex32", "hex38", "hex44", "hex50", "hex56")
Thesis_scale <- Thesis_scale %>%
  mutate(cons_score = rowMeans(Thesis_scale[,cons],na.rm=TRUE)) 
cons_items <- Thesis_scale[, cons]
cronbach.alpha(cons_items, standardized = TRUE, CI = TRUE, na.rm = TRUE)

##Openness to Experience
open <- c("hex1", "hex7", "hex13", "hex19", "hex25", "hex31", "hex37", "hex43", "hex49", "hex55")
Thesis_scale <- Thesis_scale %>%
  mutate(open_score = rowMeans(Thesis_scale[,open],na.rm=TRUE)) 
open_items <- Thesis_scale[, open]
cronbach.alpha(open_items, standardized = TRUE, CI = TRUE, na.rm = TRUE)

##Intellectual Humility Scale
ihs <- c("IHS_1", "IHS_2", "IHS_3", "IHS_4", "IHS_5", "IHS_6")
Thesis_scale <- Thesis_scale %>%
  mutate(ihs_score = rowMeans(Thesis_scale[,ihs],na.rm=TRUE)) 
ihs_items <- Thesis_scale[, ihs]
cronbach.alpha(ihs_items, standardized = TRUE, CI = TRUE, na.rm = TRUE)

##Need for Closure
nclos <- c("nclos1", "nclos2", "nclos3", "nclos4", "nclos5", "nclos6", "nclos7", "nclos8", "nclos9", "nclos10", 
                                                 "nclos11", "nclos12", "nclos13", "nclos14", "nclos15", 
                                                 "nclos16", "nclos17", "nclos18", "nclos19", "nclos20", 
                                                 "nclos21", "nclos22", "nclos23", "nclos24", "nclos25", 
                                                 "nclos26", "nclos27", "nclos28", "nclos29", "nclos30", 
                                                 "nclos31", "nclos32", "nclos33", "nclos34", "nclos35", 
                                                 "nclos36", "nclos37", "nclos38", "nclos39", "nclos40", 
                                                 "nclos41", "nclos42")
Thesis_scale <- Thesis_scale %>%
  mutate(nclos_score = rowMeans(Thesis_scale[,nclos],na.rm=TRUE)) 
nclos_items <- Thesis_scale[, nclos]
cronbach.alpha(nclos_items, standardized = TRUE, CI = TRUE, na.rm = TRUE)

##Need for Cognition
ncog <- c("ncog7", "ncog8", "ncog9", "ncog10", "ncog11", "ncog12", 
                                               "ncog13", "ncog14", "ncog15", "ncog16", "ncog17", "ncog18")
Thesis_scale <- Thesis_scale %>%
  mutate(ncog_score = rowMeans(Thesis_scale[,ncog],na.rm=TRUE)) 
ncog_items <- Thesis_scale[, ncog]
cronbach.alpha(ncog_items, standardized = TRUE, CI = TRUE, na.rm = TRUE)

##Actively Open Thinking Style
openTS <- c("A4CTS_1", "A4CTS_2", "A4CTS_3", "A4CTS_4", "A4CTS_5", "A4CTS_6")
Thesis_scale <- Thesis_scale %>%
  mutate(openTS_score = rowMeans(Thesis_scale[,openTS],na.rm=TRUE)) 
openTS_items <- Thesis_scale[, openTS]
cronbach.alpha(openTS_items, standardized = TRUE, CI = TRUE, na.rm = TRUE)

##Close-minded Thinking Style
closeTS <- c("A4CTS_7", "A4CTS_8", "A4CTS_9", "A4CTS_10", "A4CTS_11", "A4CTS_12")
Thesis_scale <- Thesis_scale %>%
  mutate(closeTS_score = rowMeans(Thesis_scale[,closeTS],na.rm=TRUE)) 
closeTS_items <- Thesis_scale[, closeTS]
cronbach.alpha(closeTS_items, standardized = TRUE, CI = TRUE, na.rm = TRUE)

##prefer intuitive Thinking Style
intuitiveTS <- c("A4CTS_13", "A4CTS_14", "A4CTS_15", "A4CTS_16", "A4CTS_17", "A4CTS_18")
Thesis_scale <- Thesis_scale %>%
  mutate(intuitiveTS_score = rowMeans(Thesis_scale[,intuitiveTS],na.rm=TRUE)) 
intuitiveTS_items <- Thesis_scale[, intuitiveTS]
cronbach.alpha(intuitiveTS_items, standardized = TRUE, CI = TRUE, na.rm = TRUE)

##prefer effortful Thinking Style
effortTS <- c("A4CTS_19", "A4CTS_20", "A4CTS_21", "A4CTS_22", "A4CTS_23", "A4CTS_24")
Thesis_scale <- Thesis_scale %>%
  mutate(effortTS_score = rowMeans(Thesis_scale[,effortTS],na.rm=TRUE)) 
effortTS_items <- Thesis_scale[, effortTS]
cronbach.alpha(effortTS_items, standardized = TRUE, CI = TRUE, na.rm = TRUE)

##Actively Open-Minded Thinking about Evidence Scale 
activeopen <- c("aopen1", "aopen2", "aopen3", "aopen4", "aopen5", "aopen6", "aopen7", "aopen8")
Thesis_scale <- Thesis_scale %>%
  mutate(activeopen_score = rowMeans(Thesis_scale[,activeopen],na.rm=TRUE)) 
activeopen_items <- Thesis_scale[, activeopen]
cronbach.alpha(activeopen_items, standardized = TRUE, CI = TRUE, na.rm = TRUE)

##Faith in Intuition Scale
fi <- c("fi1", "fi2", "fi3", "fi4", "fi5", "fi6", "fi7", "fi8", "fi9", "fi10", "fi11", "fi12")
Thesis_scale <- Thesis_scale %>%
  mutate(fi_score = rowMeans(Thesis_scale[,fi],na.rm=TRUE)) 
fi_items <- Thesis_scale[, fi]
cronbach.alpha(fi_items, standardized = TRUE, CI = TRUE, na.rm = TRUE)

## The descriptives information for each scales
psych::describe(Thesis_scale %>% select(BFS_score, BFSe_score, BFSp_score, BPS_score, LIE_score, sdtnarc_score, sdtmach_score, sdtpsych_score, narc_score, mach_score, psycho_score, psychopri_score, psychosec_score, se_score, hon_score, emo_score, extra_score, agree_score, cons_score, open_score, ihs_score, nclos_score, ncog_score, openTS_score, closeTS_score, intuitiveTS_score, effortTS_score, activeopen_score, fi_score, crt_score, word_score, NS_score))
```

## Step 2: Demographic information
For this part, I would like to know the demographic information so I might be able to use for exploratory analysis. I selected the variables I am interested in, including: gender, year in college, major, and if the participant is currently a member of a fraternity or sorority.

###Gender
```{r gender}
##For gender, I would like to do a pie chart. So I will start with coverting gender codes to labels
Thesis_scale$gender_label <- factor(Thesis_scale$gender,
                                    levels = c(1, 2, 3),
                                    labels = c("Male", "Female", "Non-binary"))
##Then I create a summary table for further plotting
genders <- Thesis_scale %>%
  count(gender_label) %>%
  mutate(perc = round(n / sum(n) * 100, 1), 
         label = paste0(perc, "%"))
##Now I can create the pie chart 
ggplot(genders, aes(x = "", y = n, fill = gender_label)) +
  geom_bar(width = 1, stat = "identity") +
  coord_polar("y") + 
  labs(title = "Participant Gender Distribution") +
  scale_fill_manual(values = c("Male" = "#90D6FF",       
                               "Female" = "#ff69b4",   
                               "Non-binary" = "#6c08db") 
                    )+
  geom_text(aes(label = label), 
            position = position_stack(vjust = 0.5), 
            color = "white", size = 5)+
  theme_void()

```

###Year in college

```{r year in college}
##For year in college, I would like to do a pie chart. So I will start with coverting gender codes to labels
Thesis_scale$year_label <- factor(Thesis_scale$year,
                                  levels = c(1, 2, 3, 4),
                                  labels = c("Freshman", "Sophomore", "Junior", "Senior"))
years <- Thesis_scale %>%
  count(year_label)

##Now I can create a bar chart
ggplot(years, aes(x = year_label, y = n, fill = year_label)) +
  geom_col() +
  geom_text(aes(label = n), vjust = -0.5, size = 3) +
  labs(title = "Participants by Year in College",
       x = "Year in College",
       y = "Number of Participants") +
  scale_fill_manual(values = c("#7a4d9f", "#eb68a0", "#feb326", "#64c5eb")) +
  theme_minimal() +
  theme(legend.position = "none")
```

###Greek Life

```{r}
##Although this is not the focus of my thesis study, I asked the participants if they are currently a member of a fraternity or sorority. I added this question just want to explore if certain personality traits might be related with one's greek life involvement.  
##In terms of visualization, I want to present gender and involvement in greek life.

Thesis_scale <- Thesis_scale %>%
  mutate(
    greek = factor(Greek1, levels = c(1, 2),
                         labels = c("Not Involved", "Greek Life"))
  )

##count combinations
gender_greek <- Thesis_scale %>%
  count(gender_label, greek)

##create the bar chart
ggplot(gender_greek, aes(x = gender_label, y = n, fill = greek)) +
  geom_col(position = "dodge") +
  labs(title = "Greek Life Involvement by Gender",
       x = "Gender",
       y = "Number of Participants",
       fill = "Greek Life") +
  scale_fill_manual(values = c("Not Involved" = "#FFDE21", "Greek Life" = "#64c5eb")) +
  theme_minimal() +
  coord_flip()
```

Looking at the graph, I can tell that most of the students in the study are involved in greek life. In addition, the number of male students involved in a fraternity is more than twice the number of male students who are not involved in Greek life. For the two non-binary students, both of them are involed in greek life. 

```{r}
## Now I would like to add year in college as another vairable for visualization. I want to know whether male students are more involved in greek life despite of year in college

##I start with combining
gender_year_greek <- Thesis_scale %>%
  count(year_label, gender_label, greek)

##And then I grouped bars by gender and greek life involvement, faceted by year in college
ggplot(gender_year_greek, aes(x = gender_label, y = n, fill = greek)) +
  geom_col(position = "dodge") +
  facet_wrap(~ year_label) +
  labs(title = "Greek Life Involvement by Gender and Year",
       x = "Gender",
       y = "Number of Participants",
       fill = "Greek Life") +
  scale_fill_manual(values = c("Not Involved" = "#FFDE21", "Greek Life" = "#64c5eb")) +
  theme_minimal()
```

We can see that for both female and male freshman students at Wake, most of them are members of a sorority or a fraternity. However, for sophomore, junior, and senior, the difference between the number of students that are involved or not involved in greek life is smaller. Sophomore male students are slightly more likely to be involved in greek life, while there is still a significantly larger proportion of female students involving in greek life. 

```{r save}
saveRDS(Thesis_scale, file = "Thesis_scale.rds")
```

