---
title: "Portfolio 5"
---

> The projects should be numbered consecutively (i.e., in the order in which you began them), and should include for each project a description of the goal, the product (computer program, hand graph, computer graph, etc.), the data, and some interpretation. Reports must be reproducible and of high quality in terms of writing, grammar, presentation, etc.

## exploratory by using this dataset? Such as scale fit, moderation, or other predicting ones. \

exploratory data

gender moderation?
short answer analysis
 verbal reasoning skills serves as a moderator in the relations between facets of Machiavellianism and “bullshit” production.

lying as another variable that correlated with the other bs measures.

BPS scale exploratory factor analysis?-- is the three scales measuring the same thing for BS or different apsects 

```{r}

library(ggsignif)
library(tibble)
library(ggplot2)
library(psych)
library(ltm)
library(tidyverse)
library(ppcor)


Thesis_scale <- readRDS("Thesis_scale.rds")
```


```{r bar graph for dark traid}

# Sample data: Replace these values with your actual correlation values

dark <- data.frame(
  Trait = rep(c("MACH-short", "NARC-short", "PSYC-short", "MPI", "HSNS", "NPI", "LSRP", "LSRP-prim","LSRP-sec"), each = 3),
  Measures = rep(c("BFS", "BPS", "Thought Task"), times = 9),
  Correlation = c(0.24, 0.11, 0.09,     # Machiavellianism correlations
                  0.15, 0.08, 0.01,     # Narcissism correlations
                  0.14, 0.18, 0.01,     # Psychopathy correlations
                  .26, .18, .11, #MPI
                  .25, .07, .10,    #HSNS
                  .15, .18, .01,     #NPI
                  .18, .26, .06,      #LSRP 
                  .17, .21, .05,
                  .15, .25, .04
                  )     
  )

dark$Trait <- factor(dark$Trait, levels = c(
  "MACH-short", "MPI", "NARC-short", "HSNS", "NPI", "PSYC-short", "LSRP", "LSRP-prim","LSRP-sec"
))

plot <- ggplot(dark, aes(x = Trait, y = Correlation, fill = Measures)) +
  geom_bar(stat = "identity", position = position_dodge(width = 0.85), width = 0.8) +
  scale_fill_manual(values = c("BFS" = "#1f77b4", "BPS" = "#ff7f0e", "Thought Task" = "#2ca02c")) +
  theme_classic(base_size = 12) + # Set the base font size to 12
  theme(
    text = element_text(family = "Times New Roman"), # Use Times New Roman for all text
    plot.title = element_text(size = 12, face = "bold", hjust = 0.5),
    axis.title = element_text(size = 12, face = "bold", hjust = 0.5),
    axis.text = element_text(size = 12),
    legend.title = element_text(size = 12),
    legend.text = element_text(size = 12)
  ) +
  labs(
    title = " ",
    x = "Dark Triad Traits",
    y = "Partial Correlation (r)",
    fill = "Measures"
  ) +
  scale_y_continuous(limits = c(0, 0.40), expand = c(0, 0))


# Display the plot
print(plot)


```


```{r Other personality traits}
#Sample data: Replace these values with your actual correlation values
hexaco <- data.frame(
  othertrait = rep(c("HON", "EMO", "EXTRA", "AGRE", "CONS", "OPEN", "NCOG", "NCLS"), each = 3),
  Measures = rep(c("BFS", "BPS", "Thought Task"), times = 8),
  Correlation = c(-.24, -.16, -.10,   
                  .10, -.08, .04,     
                  .01, .07, .03,     
                  -.13, -.03, -.03, 
                  -.17, -.29, -.02,    
                  -.03, -.18, -.08,     
                  -.02, -.30, -.13,
                  .04, -.15, -.05)          
  )

hexaco$othertrait <- factor(hexaco$othertrait, levels = c(
  "HON", "EMO", "EXTRA", "AGRE", "CONS", "OPEN", "NCOG", "NCLS"
))

plot <- ggplot(hexaco, aes(x = othertrait, y = Correlation, fill = Measures)) +
  geom_bar(stat = "identity", position = position_dodge(width = 0.85), width = 0.8) +
  scale_fill_manual(values = c("BFS" = "#1f77b4", "BPS" = "#ff7f0e", "Thought Task" = "#2ca02c")) +
  theme_classic(base_size = 12) + # Set the base font size to 12
  theme(
    text = element_text(family = "Times New Roman"), # Use Times New Roman for all text
    plot.title = element_text(size = 12, face = "bold", hjust = 0.5),
    axis.title = element_text(size = 12, face = "bold", hjust = 0.5),
    axis.text = element_text(size = 12),
    legend.title = element_text(size = 12),
    legend.text = element_text(size = 12)
  ) +
  labs(
    title = " ",
    x = "Other Personality Traits",
    y = "Partial Correlation (r)",
    fill = "Measures"
  ) +
  scale_y_continuous(limits = c(-.40, 0.40), expand = c(0, 0))


# Display the plot
print(plot)

```


```{r Cognitive Ability}
cogability <- data.frame(
  cogab = rep(c("WORD", "NS", "CRT"), each = 3),
  Measures = rep(c("BFS", "BPS", "Thought Task"), times = 3),
  Correlation = c(-.00, -.12, .01,   
                  -.10, -.07, -.06,     
                  -.11, -.08, -.07)          
  )

cogability$cogab <- factor(cogability$cogab, levels = c(
  "WORD", "NS", "CRT"
))

plot_cog <- ggplot(cogability, aes(x = cogab, y = Correlation, fill = Measures)) +
  geom_bar(stat = "identity", position = position_dodge(width = 0.85), width = 0.8) +
  scale_fill_manual(values = c("BFS" = "#1f77b4", "BPS" = "#ff7f0e", "Thought Task" = "#2ca02c")) +
  theme_classic(base_size = 12) + # Set the base font size to 12
  theme(
    text = element_text(family = "Times New Roman"), # Use Times New Roman for all text
    plot.title = element_text(size = 12, face = "bold", hjust = 0.5),
    axis.title = element_text(size = 12, face = "bold", hjust = 0.5),
    axis.text = element_text(size = 12),
    legend.title = element_text(size = 12),
    legend.text = element_text(size = 12)
  ) +
  labs(
    title = " ",
    x = "Cognitive Ability",
    y = "Partial Correlation (r)",
    fill = "Measures"
  ) +
  scale_y_continuous(limits = c(-.40, 0.10), expand = c(0, 0))

# Display the plot
print(plot_cog)
```


```{r thinking styles}
thinkstyles <- data.frame(
  thinkst = rep(c("ACT", "PIT", "PET", "CMT", "AOT", "FI"), each = 3),
  Measures = rep(c("BFS", "BPS", "Thought Task"), times = 6),
  Correlation = c(-.14, -.37, -.06, 
                  .16, .18, -.04,
                  -.10, -.34, -.06,     
                  .09, .13, -.06,
                  -.23, -.34, -.03,
                  .14, .00, -.03)          
  )

thinkstyles$thinkst <- factor(thinkstyles$thinkst, levels = c(
  "ACT", "PIT", "PET", "CMT", "AOT", "FI"
))

plot_style <- ggplot(thinkstyles, aes(x = thinkst, y = Correlation, fill = Measures)) +
  geom_bar(stat = "identity", position = position_dodge(width = 0.85), width = 0.8) +
  scale_fill_manual(values = c("BFS" = "#1f77b4", "BPS" = "#ff7f0e", "Thought Task" = "#2ca02c")) +
  theme_classic(base_size = 12) + # Set the base font size to 12
  theme(
    text = element_text(family = "Times New Roman"), # Use Times New Roman for all text
    plot.title = element_text(size = 12, face = "bold", hjust = 0.5),
    axis.title = element_text(size = 12, face = "bold", hjust = 0.5),
    axis.text = element_text(size = 12),
    legend.title = element_text(size = 12),
    legend.text = element_text(size = 12)
  ) +
  labs(
    title = " ",
    x = "Thinking Styles",
    y = "Partial Correlation (r)",
    fill = "Measures"
  ) +
  scale_y_continuous(limits = c(-.40, 0.40), expand = c(0, 0))

# Display the plot
print(plot_style)
```


```{r self-esteem}
selfesteem <- data.frame(
  selfes = rep(c("SE"), each = 5),
  Measures = rep(c("BFSe", "BFSp", "BFS", "BPS", "Thought Task"), times = 1),
  Correlation = c(-.12, -.04, -.08, -.00, -.03)          
  )

plot_style <- ggplot(selfesteem, aes(x = selfes, y = Correlation, fill = Measures)) +
  geom_bar(stat = "identity", position = position_dodge(width = 0.85), width = 0.8) +
  scale_fill_manual(values = c("BFS" = "#1f77b4", "BPS" = "#ff7f0e", "Thought Task" = "#2ca02c", "BFSe" = "#FEDF05", "BFSp" = "#9966cc")) +
  theme_classic(base_size = 12) + # Set the base font size to 12
  theme(
    text = element_text(family = "Times New Roman"), # Use Times New Roman for all text
    plot.title = element_text(size = 12, face = "bold", hjust = 0.5),
    axis.title = element_text(size = 12, face = "bold", hjust = 0.5),
    axis.text = element_text(size = 12),
    legend.title = element_text(size = 12),
    legend.text = element_text(size = 12)
  ) +
  labs(
    title = " ",
    x = "Self-Esteem",
    y = "Partial Correlation (r)",
    fill = "Measures"
  ) +
  scale_y_continuous(limits = c(-.40, 0.20), expand = c(0, 0))

# Display the plot
print(plot_style)
```


```{r}
##install.packages("lavaan")
##install.packages("semPlot")

library(lavaan)
library(semPlot)

one_factor_model <- '
    General_Factor =~ BFS_1 + BFS_2 + BFS_3 + BFS_4 + BFS_5 + BFS_6 + BFS_7 + BFS_8 + BFS_9 + BFS_10 + BFS_11 + BFS_12 + BPS_1 + BPS_2 + BPS_3 + BPS_4 + BPS_5 + BPS_6 + BPS_7 + BPS_8 + BPS_9 + BPS_10 + BPS_11 + BPS_12
'

one_factor_fit <- cfa(one_factor_model, data = Thesis_scale)
summary(one_factor_fit, fit.measures = TRUE, standardized = TRUE)



two_factor_model <- '
    BFS_Factor =~ BFS_1 + BFS_2 + BFS_3 + BFS_4 + BFS_5 + BFS_6 + BFS_7 + BFS_8 + BFS_9 + BFS_10 + BFS_11 + BFS_12
    BPS_Factor =~ BPS_1 + BPS_2 + BPS_3 + BPS_4 + BPS_5 + BPS_6 + BPS_7 + BPS_8 + BPS_9 + BPS_10 + BPS_11 + BPS_12
'

two_factor_fit <- cfa(two_factor_model, data = Thesis_scale)
summary(two_factor_fit, fit.measures = TRUE, standardized = TRUE)


#Compare models:
compare_models <- anova(one_factor_fit, two_factor_fit)
print(compare_models)

semPaths(one_factor_fit, what = "std", layout = "tree", edge.label.cex = 1.2, title = FALSE)
semPaths(two_factor_fit, what = "std", layout = "tree", edge.label.cex = 1.2, title = FALSE)
```
```{r}
#install.packages("psych")
#install.packages("GPArotation")
library(psych)
library(GPArotation)

# Preparing the data: Assuming your items are named BFS1, BFS2, ..., BPS1, BPS2, ...
# Select all BFS and BPS items for the analysis
bfs_it <- paste0("BFS_", 1:12)
bps_it <- paste0("BPS_", 1:12)

all_items <- c(bfs_it, bps_it)

# Select the relevant columns from your dataset
efa_data <- Thesis_scale[, all_items]

# Check if the data is suitable for EFA (KMO and Bartlett’s test)
KMO(efa_data)  # Should be > 0.60 for a good EFA
cortest.bartlett(efa_data)  # Should be significant (p < .05)

bartlett_result <- cortest.bartlett(efa_data)
print(bartlett_result)  # Should be significant (p < .05)




# Principal Component Analysis (PCA) to determine number of factors
pca_results <- principal(efa_data, nfactors = ncol(efa_data), rotate = "none")
print(pca_results$values)

# Scree Plot (to visualize eigenvalues)
scree(efa_data)

# Parallel Analysis (more reliable than scree plot alone)
fa.parallel(efa_data, fa = "fa", n.iter = 100)




# Run EFA for 2 Factors
efa_2factor <- fa(efa_data, nfactors = 3, rotate = "oblimin", fm = "ml")

# Print results
print(efa_2factor)

# Visualize factor loadings
fa.diagram(efa_2factor)
```

```{r}
bfs_model <- '
  BFS_Factor =~ BFS_1 + BFS_2 + BFS_3 + BFS_4 + BFS_5 + BFS_6 + 
                BFS_7 + BFS_8 + BFS_9 + BFS_10 + BFS_11 + BFS_12
'

# Fit the model
bfs_fit <- cfa(bfs_model, data = Thesis_scale)
summary(bfs_fit, fit.measures = TRUE, standardized = TRUE)

# Visualize the model
semPaths(bfs_fit, what = "std", layout = "tree", edge.label.cex = 1.2)
```

```{r}
# Specify a single-factor model for BPS
bps_model <- '
  BPS_Factor =~ BPS_1 + BPS_2 + BPS_3 + BPS_4 + BPS_5 + BPS_6 + 
                BPS_7 + BPS_8 + BPS_9 + BPS_10
'

# Fit the model
bps_fit <- cfa(bps_model, data = Thesis_scale)
summary(bps_fit, fit.measures = TRUE, standardized = TRUE)

# Visualize the model
semPaths(bps_fit, what = "std", layout = "tree", edge.label.cex = 1.2)
```

```{r}
bfs_it <- paste0("BFS_", 1:12)
lie_it <- paste0("lies", 1:14)

all_items_liebfs <- c(bfs_it, lie_it)

# Select the relevant columns from your dataset
efa_data_liebfs <- Thesis_scale[, all_items_liebfs]

# Check if the data is suitable for EFA (KMO and Bartlett’s test)
KMO(efa_data_liebfs)  # Should be > 0.60 for a good EFA
cortest.bartlett(efa_data_liebfs)  # Should be significant (p < .05)

liebfs_result <- cortest.bartlett(efa_data_liebfs)
print(liebfs_result)  # Should be significant (p < .05)


# Principal Component Analysis (PCA) to determine number of factors
pcalie_results <- principal(efa_data_liebfs, nfactors = ncol(efa_data_liebfs), rotate = "none")
print(pcalie_results$values)

# Scree Plot (to visualize eigenvalues)
scree(efa_data_liebfs)

# Parallel Analysis (more reliable than scree plot alone)
fa.parallel(efa_data_liebfs, fa = "fa", n.iter = 100)


# Run EFA for 3 Factors
efa_2factorlie <- fa(efa_data_liebfs, nfactors = 3, rotate = "oblimin", fm = "ml")

# Print results
print(efa_2factorlie)

# Visualize factor loadings
fa.diagram(efa_2factorlie)


# Run EFA for 4 Factors
efa_2factorlie <- fa(efa_data_liebfs, nfactors = 4, rotate = "oblimin", fm = "ml")

# Print results
print(efa_2factorlie)

# Visualize factor loadings
fa.diagram(efa_2factorlie)

```


